Adaptive Hierarchical Sliding Mode Control with Input Saturation for Attitude Regulation of Multi-satellite Tethered System

### 2016-07-03 manuscript.tex
20160703

To alleviate these concerns of the thruster-based control, some alternative non-pure thruster-based schemes for formation flights of the TSS have been proposed. Miller addressed the concept of the electromagnetic formation flying (EMFF), in which the high temperature superconducting technology was employed to regulate the attitude indirectly~\cite{miller2010control}. Some researches followed to achieve EMFF by using different control schemes~\cite{zhang2014adaptive,huang2015lmi}. Yang investigated the three-inline satellite array, in which the participating satellites were equipped with the reaction wheels and the thrusters, and hence the linear force and the flywheel torque cooperated to manipulate the spacecraft~\cite{yang2015decentralized}. Natarajan and Schaub combined the Coulomb forces with conventional thrust forces to obtain a control scheme, in which the Coulomb forces predominated, and investigated the stability of the two-craft formation about different equilibrium configurations~\cite{natarajan2009hybrid}. In the view of canceling the drawback of the thrusters in the attitude regulation control, as a inter-force actuator, the utilization of flywheels has been focused on~\cite{pizarro2008dynamics}. Comparing to the thruster-based scheme, the solar sails providing the power for the flywheels can achieve a long-term control, and simultaneously the contamination to the sensitive sensors does not occur. However, in the absence of the thrusters forces, the pure flywheel torque control causes the attitude dynamics underactuated adversely, i.e., Chung et al. introduced the concept of the underactuated multi-satellite inline system, and proposed the underactuated control scheme for the compound pendulum dynamics of the TSS~\cite{chung2008propellant1}.\par

@@

\end{align} \begin{color}{red}From equations above, $\omega_2$ is independent from $\omega_1$. Similar to the dynamic state $\omega_3$, dynamic state $\omega_2$ can be controlled separately without affecting the in-plane dynamics~\cite{chung2007nonlinear,chung2007nonlinear1,chung2007nonlinear3}. For each satellite, three flywheels are mounted orthogonally to regulate the attitude. The flywheel which is mounted perpendicularly to the tether, governs the dynamic state $\omega_3$, and different from the other axes, the varying $\omega_3$ will not lead to the situation described in Figure~\ref{Figure:model3body}, hence a simple linear feedback control can achieve its attitude regulation. When we attention on the in-plane dynamics, the other two flywheel torques and thruster firing handle the out-plane dynamics, which can guarantee that the in-plane motion occurs without other disturbance from the other axes.\end{color} On the premise of the assumption that the out-of-plane plant is stable independently, the in-plane attitude dynamics, accordingly, can be described as a model consisting of three flywheels assembly and two tethers, as seen in Figure~\ref{Figure:model3body}. The mathematical model expressed by using Euler¨CLagrange equations is established, and the origin of the array is the satellite's geometrical center as well the mass center. In the 2D plane, the three-body satellite array arranges along the $y$ direction, and the positive directions of $\theta_i$ and $\phi_i$ are anticlockwise. $F_i$ denotes the $i$th thruster's linear force, and $u_i$ is defined to be the $i$th flywheel torque acting on the center of mass. $\Psi$ identifies the rotation angle, then the dynamic equation follows~\cite{chung2007nonlinear1}

@@

In above equations, $r$ and $l$ denote the radius of the satellite and tether length, respectively. The tether connecting point's moment of inertia is known as $I_r=I_G+mr^2$.

@@

and $\delta>1$. The derivative of $\eta(t)$ has the characteristics $$\dot{{\eta}}(t) = \rho\gamma\delta e^{-2\gamma^{-1}{\eta}^{-1}(t)}\vert S\vert$$ and $\eta(0) > 0$ so that the $\eta(t)$ is constant positive. $\gamma$ is a parameter for cancelling the input saturation, and it will be discussed later on. Hence the crucial theorem is given.

@@

Moreover, term $R(u)\rho\delta\eta(t)\vert S\vert$ is positive, and $0< R(u)\le 1$. The Inequality.~(\ref{eq:dotV}) becomes the interim form:

@@

@@

In preceding equation

@@

The situation of the attitude regulation is illustrated in Figure~\ref{Figure:attitude}, in which the array angular rate is adjusted to be the desired value from the initial condition so that the individual satellites and the central satellite are rotating together at the same velocity. It is at about 1.2 $s$ when the trajectory of the attitude angle converges to the preset value, $\phi_d = 0$, so does the array angular rate. \begin{color}{red}The performance of the decentralized control reported in~\cite{chung2008propellant1} is also illustrated in Figure~\ref{Figure:attitude}. In~\cite{chung2008propellant1}, a pair of thrusters are used to dump the angular momentum caused by the saturation of the flywheel speed, and for reducing the consumption of thruster firing, a little gain design is demanded in the decentralized control strategy. Hence, the decentralized control inevitably leads to a slow smooth attitude regulation shown in Figure~\ref{Figure:attitude}. Compared with the the decentralized control scheme, one can find that the MHSM control demonstrates a fast regulation, and although the amplitudes of the varying attitude angle and the array angular rate of the MHSM control are greater with the variations falling in $[-0.05,0.2]$ $rad$ and $[0.225,0.375]$ $rad/s$, respectively, this variations are tolerable in some fast attitude scenarios of the TSS~\cite{Williams2009745}. Even the input saturation occurs during the attitude regulation, the MHSM control scheme guarantees the stability of the system, and hence the selection of the gain is flexible so that the performance of the control system can be adjusted by the suitable parameters. \end{color}\par

>>>>

To alleviate these concerns of the thruster-based control, some alternative non-pure thruster-based schemes for formation flights of the TSS have been proposed. Miller addressed the concept of the electromagnetic formation flying (EMFF), in which the high temperature superconducting technology was employed to regulate the attitude indirectly~\cite{miller2010control}. Some researches followed to achieve EMFF by using different control schemes~\cite{zhang2014adaptive,huang2015lmi}. \begin{color}{red}Zhong et al. reported the application of electrodynamic tether for nanosatellite fast deorbit in low earth orbit~\cite{zhong2013dynamics}, and also presented a piecewise two-phased optimal control scheme to achieve open-loop control trajectory optimization~\cite{zhong2014optimal}.\end{color} Yang investigated the three-inline satellite array, in which the participating satellites were equipped with the reaction wheels and the thrusters, and hence the linear force and the flywheel torque cooperated to manipulate the spacecraft~\cite{yang2015decentralized}. Natarajan and Schaub combined the Coulomb forces with conventional thrust forces to obtain a control scheme, in which the Coulomb forces predominated, and investigated the stability of the two-craft formation about different equilibrium configurations~\cite{natarajan2009hybrid}. In the view of canceling the drawback of the thrusters in the attitude regulation control, as a inter-force actuator, the utilization of flywheels has been focused on~\cite{pizarro2008dynamics}. Comparing to the thruster-based scheme, the solar sails providing the power for the flywheels can achieve a long-term control, and simultaneously the contamination to the sensitive sensors does not occur. However, in the absence of the thrusters forces, the pure flywheel torque control causes the attitude dynamics underactuated adversely, i.e., Chung et al. introduced the concept of the underactuated multi-satellite inline system, and proposed the underactuated control scheme for the compound pendulum dynamics of the TSS~\cite{chung2008propellant1}.\par

@@

\end{align} \begin{color}{red}From equations above, $\omega_2$ is independent from $\omega_1$. Similar to the dynamic state $\omega_3$, dynamic state $\omega_2$ can be controlled separately without affecting the in-plane dynamics~\cite{chung2007nonlinear,chung2007nonlinear1,chung2007nonlinear3}. For each satellite, three flywheels are mounted orthogonally to regulate the attitude. The flywheel which is mounted perpendicularly to the tether, governs the dynamic state $\omega_3$, and different from the other axes, the varying $\omega_3$ will not lead to the situation described in Figure~\ref{Figure:model3body}, hence a simple linear feedback control can achieve its attitude regulation. When we attention on the in-plane dynamics, the other two flywheel torques and thruster firing handle the out-plane dynamics, which can guarantee that the in-plane motion occurs without other disturbance from the other axes.\end{color} On the premise of the assumption that the out-of-plane plant is stable independently, the in-plane attitude dynamics, accordingly, can be described as a model consisting of three flywheels assembly and two tethers, as seen in Figure~\ref{Figure:model3body}. \begin{color}{red}The mathematical model expressed by using Euler-Lagrange equations is established, and the origin of the array is the satellite's geometrical center as well the mass center.\end{color} In the 2D plane, the three-body satellite array arranges along the $y$ direction, and the positive directions of $\theta_i$ and $\phi_i$ are anticlockwise. $F_i$ denotes the $i$th thruster's linear force, and $u_i$ is defined to be the $i$th flywheel torque acting on the center of mass. $\Psi$ identifies the rotation angle, then the dynamic equation follows~\cite{chung2007nonlinear1}

@@

In above equations, $r$ and $l$ denote the radius of the satellite and tether length, respectively. The tether connecting point's moment of inertia is known as $I_r=I_G+mr^2$. \begin{color}{red}Consider matrix determinant of $M_1$
\vert M_1\vert
&= (I_r+ml^2+2mrl\cos{\phi})I_r-(I_r+mrl\cos{\phi})^2\\
&= I_rml^2 - m^2r^2l^2\cos^2{\phi}.
Hence $\vert M_1\vert = I_gml^2+m^2r^2l^2(1-\cos^2{\phi})>0$, and $M_1$ is invertible. In the view of Lagrangian mechanics, one can get the similar result, since $M_{1}$ is a positive definite matrix~\cite{ortega2013passivity}.\end{color}

@@

and $\delta>1$. The derivative of $\eta(t)$ has the characteristics $$\dot{{\eta}}(t) = \rho\gamma\delta e^{-2\gamma^{-1}{\eta}^{-1}(t)}\vert S\vert$$ and $\eta(0) > 0$ so that the $\eta(t)$ is constant positive. $\gamma$ is a parameter for cancelling the input saturation, and it will be discussed later on. \begin{color}{red}
For voiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $\alpha=\beta>0$. One can check that $\alpha b_1(X,t)+\beta b_2(X,t)$ is positive to get non-singular the input,
    \alpha b_1(X,t)+\beta b_2(X,t) &= \alpha(b_1(X,t)+b_2(X,t))\\
    &=\frac{\alpha(-mrl\cos x_3+mrl\cos x_3+ml^2)}{I_rml^2-m^2r^2l^2\cos{^2x_3}}\\
    &=\frac{\alpha ml^2}{I_rml^2-m^2r^2l^2\cos{^2x_3}}>0.
    Moreover, according to the derivation above, selecting $\alpha$ and $\beta$ with $\beta>\alpha>0$ yields 
    \alpha b_1(X,t)+\beta b_2(X,t) &= \alpha(b_1(X,t)+b_2(X,t))+(\beta-\alpha)b_2(X,t)\\
    &=\frac{(\beta-\alpha)mrl\cos x_3 + \beta ml^2}{I_rml^2-m^2r^2l^2\cos{^2x_3}}>0.
    This can also guarantee the non-singularity of Eq.~(\ref{eq:u}), because $x_3$ should be varying in a small region with $\vert x_3\vert<\pi/2$.

@@

Moreover, term $R(u)\rho\delta\eta(t)\vert S\vert$ is positive, and $0< R(u)\le 1$. \begin{color}{red}The inequality.~(\ref{eq:dotV}) becomes the interim form:\end{color}

@@

\begin{color}{red}Consider the denominator of $M_3^{-1}(x_3,x_5)$:
I_rml^2(2I_r-mr^2\cos{^2\phi_1}-mr^2\cos{^2\phi_2})
&= I_rml^2(2I_g+2mr^2-mr^2\cos{^2\phi_1}-mr^2\cos{^2\phi_2})\\
&= I_rml^2[2I_g+mr^2(1-\cos{^2\phi_1})+mr^2(1-\cos{^2\phi_2})]>0
where $\vert\phi_1\vert<\pi/2$, $\vert\phi_2\vert<\pi/2$. Hence $M_{3}$ is invertible.\end{color}\par

@@

For voiding the singularity of the inputs, the parameter $\bar\alpha$, $\bar\beta$ and $\bar\iota$ should satisfy the the condition $\bar\alpha=\bar\beta=\bar\iota>0$. Consider the denominator of the input $u_1$:
    &\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)\\
    =&\bar\alpha(b_1(X,t) + b_3(X,t) + b_5(X,t))\\
    =&\bar\alpha(2ml^2I_r-m^2r^2l^2\cos^2\phi_2+I_rmrl\cos\phi_1+m^2r^2l^2\cos\phi_2\cos\phi_1)\\
    =&\bar\alpha(ml^I_r+ml^2I_g+m^2r^2l^2(1-\cos^2\phi_2)+I_rmrl\cos\phi_1+m^2r^2l^2\cos\phi_2\cos\phi_1)
    where $\vert\phi_1\vert<\pi/2$ and $\vert\phi_2\vert<\pi/2$, and hence $\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)>0$. Also, $\bar\alpha b_2(X,t) + \bar\beta b_4(X,t) + \bar\iota b_6(X,t)>0$ can be obtained with the same derivation.
In preceding equation~(\ref{eq:u1u2})

@@

The situation of the attitude regulation is illustrated in Figure~\ref{Figure:attitude}, in which the array angular rate is adjusted to be the desired value from the initial condition so that the individual satellites and the central satellite are rotating together at the same velocity. It is at about 1.2 $s$ when the trajectory of the attitude angle converges to the preset value, $\phi_d = 0$, so does the array angular rate. \begin{color}{red}The performance of the decentralized control reported in~\cite{chung2008propellant1} is also illustrated in Figure~\ref{Figure:attitude}. In~\cite{chung2008propellant1}, a pair of thrusters are used to dump the angular momentum caused by the saturation of the flywheel speed, and for reducing the consumption of thruster firing, a little gain design is demanded in the decentralized control strategy. Hence, the decentralized control inevitably leads to a slow smooth attitude regulation shown in Figure~\ref{Figure:attitude}. Compared with the the decentralized control scheme, one can find that the MHSM control demonstrates a fast regulation, and although the amplitudes of the varying attitude angle and the array angular rate of the MHSM control are greater with the variations falling in $[-0.05,0.2]$ $rad$ and $[0.225,0.375]$ $rad/s$, respectively, this variations are tolerable in some fast attitude scenarios of the TSS~\cite{Williams2009745}. Even if the input saturation occurs during the attitude regulation, the MHSM control scheme guarantees the stability of the system, and hence the selection of the gain is flexible so that the performance of the control system can be adjusted by the suitable parameters. \end{color}\par
